### 2021-10-14 revision/ch3bedEle.tex
finished.

\begin{wraptable}{r}{0.6\textwidth}
	\caption{Migration, entrainment, and deposition rates at $z(m)=0$ are tabulated from \citet{Ancey2008}. Units are $s^{-1}$ (probability/time). Bed elevation changes modulate these rates in accord with Eqs. \ref{eq:rate1}-\ref{eq:rate4}.}\label{tab:anceyparams}
	\begin{tabular}{cccccc} \\ 
		\toprule  
		flow & $\nu$ & $\lambda$ & $\mu$ & $\sigma$ & $\gamma$ \\
		\midrule
		(a) & 5.45  & 6.59  & 3.74 & 4.67 & 0.77 \\
		\midrule
		(g) & 7.74  & 8.42  & 4.34 & 4.95 & 0.56 \\
		\midrule
		(i) & 15.56 & 22.07 & 3.56 & 4.52 & 0.68 \\
		\midrule
		(l) & 15.52 & 14.64 & 4.32 & 4.77 & 0.48 \\
		\bottomrule
	\end{tabular}
\end{wraptable}
For the migration, entrainment, and deposition parameters representing bedload transport at each flow condition $(\nu, \lambda, \mu, \sigma, \gamma)$, I used the values measured by \citet{Ancey2008} in a series of flume experiments: these are summarized in Tab. \ref{tab:anceyparams}.
Flow conditions are labeled (a), (g), (i), and (l), roughly in order of increasing bedload flux (see \citet{Ancey2008} for more details). 
In all simulations, I took the packing fraction $\phi = 0.6$ -- a typical value for a pile of spheres \citep[e.g.][]{Bennett1972}, and I set $L = 22.5$cm and $a = 0.3$cm, values from the original \citet{Ancey2008} experiments.
Each simulation was run for $250$hrs of virtual time, a period selected to ensure convergence of particle activity and bed elevation statistics.

@@

Fig. \ref{fig:var} demonstrates that the variance of bed elevations is approximately $\sigma_z^2 = z_1^2 \sigma_m^2 = \frac{1}{4\kappa}=l^2$, agreeing with the approximation in Eq. \ref{eq:ou2}; this result suggests that $l$ is a characteristic length scale of bed elevation fluctuations.
\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\textwidth,keepaspectratio]{./figures/ch3/variance.pdf}
	\caption{Data from all simulations demonstrates that the active layer depth $l$ characterizes bed elevation changes as described by Eq. \ref{eq:active}: $\sigma_m^2 \approx (l/z_1)^2$. }
	\label{fig:var}
\end{wrapfigure}
\indent The close correspondence between the mean field approximation and the numerical simulations in Fig. \ref{fig:pdfs} panel (a) suggests the unconditional moments of $n$ correspond closely with the \citet{Ancey2008} result. They appear identical within numerical uncertainty.

>>>>

\begin{table}
	\begin{center}
	\def~{\hphantom{0}}
	\begin{tabular}{c|ccccc} 
		\toprule  
		flow & $\nu$ & $\lambda$ & $\mu$ & $\sigma$ & $\gamma$ \\
		\midrule
		(a) & 5.45  & 6.59  & 3.74 & 4.67 & 0.77 \\
		(g) & 7.74  & 8.42  & 4.34 & 4.95 & 0.56 \\
		(i) & 15.56 & 22.07 & 3.56 & 4.52 & 0.68 \\
		(l) & 15.52 & 14.64 & 4.32 & 4.77 & 0.48 \\
	\end{tabular}
	\caption{Migration, entrainment, and deposition rates at $z(m)=0$ are tabulated from \citet{Ancey2008}. Units are $s^{-1}$ (probability/time). Bed elevation changes modulate these rates in accord with Eqs. \ref{eq:rate1}-\ref{eq:rate4}.}
	\label{tab:anceyparams}
	\end{center}
\end{table}

For the migration, entrainment, and deposition parameters representing bedload transport at each flow condition $(\nu, \lambda, \mu, \sigma, \gamma)$, I used the values measured by \citet{Ancey2008} in a series of flume experiments: these are summarized in Tab. \ref{tab:anceyparams}.
Flow conditions are labeled (a), (g), (i), and (l), roughly in order of increasing bedload flux (see \citet{Ancey2008} for more details). 
In all simulations, I took the packing fraction $\phi = 0.6$ -- a typical value for a pile of spheres \citep[e.g.][]{Bennett1972}, and I set $L = 22.5$cm and $a = 0.3$cm, values from the original \citet{Ancey2008} experiments.
Each simulation was run for $250$hrs of virtual time, a period selected to ensure convergence of particle activity and bed elevation statistics.

@@

\begin{figure}
	\centerline{\includegraphics{./figures/ch3/newvariance.pdf}}
	\caption{Data from all simulations demonstrates that the active layer depth $l$ characterizes bed elevation changes as described by Eq. \ref{eq:active}: $\sigma_m^2 \approx (l/z_1)^2$.}
	\label{fig:var}
\end{figure}

Fig. \ref{fig:var} demonstrates that the variance of bed elevations is approximately $\sigma_z^2 = z_1^2 \sigma_m^2 = \frac{1}{4\kappa}=l^2$, agreeing with the approximation in Eq. \ref{eq:ou2}; this result indicates that $l$ is a characteristic length scale of bed elevation fluctuations.
The close correspondence between the mean field approximation and the numerical simulations in Fig. \ref{fig:pdfs} panel (a) suggests the unconditional moments of $n$ correspond closely with the \citet{Ancey2008} result. They appear identical within numerical uncertainty.
